Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-08 paper.qmd
Update with quollr new updates

umap_scurve_scaled <- gen_scaled_data(
  data = umap_scurve, 
  x = "UMAP1", 
  y = "UMAP2", 
  hr = 2/sqrt(3))

sc_ltr_pos <- c(0.08, 0.96)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 2.59)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2)

@@

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 6
num_bins_y_scurve <- 14
hex_size_scurve <- 0.13
buffer_x_scurve <- 0.338
buffer_y_scurve <- 0.292
x_start_scurve <- -0.113
y_start_scurve <- -0.098

## Hexagonal binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  data = umap_scurve_scaled, 
  x = "UMAP1",
  y = "UMAP2", 
  num_bins_x = num_bins_x_scurve,
  num_bins_y = num_bins_y_scurve, 
  x_start = x_start_scurve,
  y_start = y_start_scurve, 
  buffer_x = buffer_x_scurve,
  buffer_y = buffer_y_scurve, 
  hex_size = hex_size_scurve,
  col_start = "UMAP")

>>>>

scurve_scaled_obj <- gen_scaled_data(
  data = umap_scurve)

umap_scurve_scaled <- scurve_scaled_obj$scaled_nldr
lim1 <- scurve_scaled_obj$lim1
lim2 <- scurve_scaled_obj$lim2
r2 <- diff(lim2)/diff(lim1)

sc_ltr_pos <- c(0.08, 0.96)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 1.9)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2)

@@

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 6

## Hexagonal binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = num_bins_x_scurve, 
  s1 = -0.06, 
  s2 = -0.06, 
  r2 = r2)
